{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}

### 2022-01-21 Paper/main.tex
Increment

	Then, the operator $K$ has orthonormal basis functions $v_{i} \in L^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator. Moreover, K holds following triats:

@@

	\subsection{Literature}
	\begin{itemize}
		\item \cite{kokoszka_introduction_2017}
		\item \cite{hsing_theoretical_2015}
		\item \cite{ramsay_functional_2005}
		\item \cite{horvath_inference_2012}
		\item \cite{cai_prediction_2006}
		\item \cite{levitin_introduction_2007}
	\end{itemize}

@@

	\subsection{Motivation}
	For the simulation study, we deviate from the standard simulation setting. Instead of generating data by ourselves, we imposed the gasoline data which consists of 60 samples of Near Infrared (NIR) spectroscopy measured by 2-nm from 900 to 1,700 nm, and a response variable, octane rate. The dataset, which contains 60 i.i.d. observations with 401 measurements, allows to analyze samples of gasoline much faster and with the same reproducibility as standard tests (cf. \cite{Bohacs_Ovadi_Salgo1998}). The optimal number L of basis functions were chosen for each model through 10-fold Cross-Validation. Additionally, even for FPCR, we discovered what number of components produces the best. As a result, we progressed the application with the derived outcomes.

@@

    {\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
    Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other. Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience... No theoretical reasoning)}

    \subsection{Simulation setup}
	The simulation study follows Reiss and Ogden (2007) as a guideline. Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1(t)$ and $f_2(t)$ were chosen that differ in their smoothness:

@@

Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by a error variation $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.

@@

		where $Z \sim \mathcal{N}(0,1)$ to test the methods with different signal-to-noise ratios. In total we create four combinations for the simulation, using the two true coefficient functions and the two sets of responses. These four combinations are then used with different number of cubic bspline basis-function $(5,6,...,25)$ and fourier functions $(1,2,...,25)$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we use 10f cross-validation. The simulation was done with R (version...). In total we carried out 2000 simulations for each combination of data and number of basis functions. {\color{green} Information about version and link to repo / package in footnote??}

>>>>

	Then, the operator $K$ has orthonormal basis functions $v_{i} \in L^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator. Moreover, $K$ holds following traits:

@@

	\subsection{Literature}
	\begin{itemize}
		\item \cite{alexanderian_KLexpansion_2015}
		\item \cite{kokoszka_introduction_2017}
		\item \cite{hsing_theoretical_2015}
		\item \cite{ramsay_functional_2005}
		\item \cite{horvath_inference_2012}
		\item \cite{cai_prediction_2006}
		\item \cite{levitin_introduction_2007}
	\end{itemize}

@@

	\subsection{Motivation}
	For the simulation study, we deviate from the standard simulation setting. Instead of generating data by ourselves, we imposed the gasoline data which consists of 60 samples of Near Infrared (NIR) spectroscopy measured by 2-nm from 900 to 1,700 nm, and a response variable, octane rate. The dataset, which contains 60 i.i.d. observations with 401 measurements, allows to analyze samples of gasoline much faster and with the same reproducibility as standard tests (cf. \cite{Bohacs_Ovadi_Salgo1998}). The optimal number L of basis functions were chosen for each model through 10-fold Cross-Validation. Additionally, even for FPCR, we discovered what number of components produces the best. We finally progressed the application with the derived outcomes from our simulation study.

@@

    %{\color{blue} I shifted this from theory to over here, as it makes more sense in the simulation part.\\
    %Very short summary: take fpc's and eigenvalues, use that the scores are independent from each other. Use the eigenvalues as variances and draw from a multivariate normal with the right varcov matrix (normal just because of convenience... No theoretical reasoning)}

    \subsection{Simulation setup}
	The simulation study follows \cite{Reiss_2007b} as a guideline. Two different true coefficient functions, smooth function $f_1(t)$ and bumpy function $f_2(t)$, were chosen to differentiate their smoothness. The bumpy function was generated by refering to \cite{cardot_bumpyfunction_2002}. The two functions are described as: {\color{orange} we might define the interval of t on the functions}

@@

		The intention of comparisons based on the two functions was to represent which type of expansions turn out better simulation results in each case where the functions are bumpy and smooth. Two different error-terms $\epsilon$ were created by first generating $i.i.d.$ standard normal error and then multiplying them by a error variation $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.

@@

		where $Z \sim \mathcal{N}(0,1)$ to test the methods with different signal-to-noise ratios. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with different number of cubic bspline basis-function $(5,6,...,25)$ and fourier functions $(1,2,...,25)$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used 10f cross-validation. The simulation was done with R (version...). We carried out 2500 repetitions for each set of simulations. {\color{green} Information about version and link to repo / package in footnote??}
